---
title: "LAB11 activity"
author: "Yingtong Lyu"
date: "November 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Write a function that generates numbers from binomial(n, p) distribution using runif() function. Hint: binomial(n, p) random variable can be defined as a sum of n independent Bernoulli(p) random variables.

```{r cars}
#use runif to generate s numbers from binomial(n,p)
set.seed(123)
n=10
p=0.5
s <- 10
x <- 0
newbinom <- function(s, n, p){
  rbi <- vector(length = s)
  for (i in 1: s) {
    rb <- as.numeric(runif(n) < p)
    rbi[i] <- sum(rb)
  }
    return(rbi)
}



newbinom(s,n,p)
rbinom(s,n,p)


```


#2. Compare performance of your function with rbinom() using microbenchmark() function.
```{r}
library(microbenchmark)
microbenchmark(rbinom(s,n,p),newbinom(s,n,p)) 
```

#3. Suppose we want to simulate data from a linear regression model:
#Yi = 0 + 1 × Xi + i i = 1, ...,N
#where   N(0, 3) and X is a covariate that ranges between 20 and 40. Let 0 = 15 and 1 = 0.4 are known coefficients. Generate data (N = 50) from this models with given coefficients. Fit a linear regression model and plot fitted values vs residuals using ggplot() function. Please do not forget to use set.seed() function for reproducibility.
```{r}
library(ggplot2)
set.seed(123)
dist <- vector(length = 50)
x <- vector(length = 50)
for (i in 1:50){
 x[i]<- runif(1,20,40)
 dist[i] <- 15 + 0.4*x[i] + rnorm(1,0,3)}
fit <- lm(dist ~ x)
ggplot(mapping = aes(fit$fitted.values,fit$residuals))+
  geom_point() +
  geom_smooth(method='lm')+
  labs(x="fitted values", y= "residuals")

```


4.
```{r}
creatrnorm <- function (n) 
    {
        U1 <- runif(n/2, 0, 1)
        U2 <- runif(n/2, 0, 1)
        x = sqrt(-2 * log(U1)) * cos(2 * pi * U2)
        y = sqrt(-2 * log(U1)) * sin(2 * pi * U2)
        z <- c(x, y)
        z
}

y1 <- creatrnorm(6000) 
y2 <- rnorm(6000)
Y <- data.frame(y1, y2)

ggplot(data=Y, aes(x= y1, fill = "1")) + 
    geom_histogram(alpha = 0.3) + 
    geom_histogram(aes(x= y2, fill = "2"), alpha = 0.3) +
    labs(x="X", y="Frequency", title = "Comparison between Box-Muller algorithm and Normal distribution ") +
    scale_fill_discrete(name = "Method", labels=c("Box-Muller Algorithm","Normal Distribution"))
```

